### 2019-04-15 README.Rmd
Update README.md

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# `robvis`: an R pacakge for quick visualisation of risk-of-bias assessment results

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%",
  fig.width= 8, 
  fig.height=3)
```
# `robvis`: an R pacakge for quick visualisation of risk-of-bias assessment results
